A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-05 tex/codatadp.tex
more

\newcommand\cheat{\vskip.75\smallskipamount} %% TYPESETTING

@@

\cheat
\item
Normal forms are needed and must be enumeratable. For finite model finding, requires a $\mu$ notation,
e.g., $\const{SCons}(3,\, \mu s.\; \const{SCons}(1,\, \const{SCons}(4,\, s)))$
represents the lasso-shaped sequence $3, 1, 4, 1, 4, \ldots$\kern0.1em. %%% TYPESETTING: kern
\end{itemize}

>>>>

\newcommand\cheat{\vskip\smallskipamount} %% TYPESETTING

@@

\cheat
\item
\emph{It must be possible to express cyclic values as closed terms and
to enumerate them.} For finite model finding, requires a $\mu$ notation,
e.g., $\const{SCons}(3,\, \mu s.\; \const{SCons}(1,\, \const{SCons}(4,\, s)))$
represents the lasso-shaped sequence $3, 1, 4, 1, 4, \ldots$\kern0.1em. %%% TYPESETTING: kern
\end{itemize}
